Technical Report

### 2018-03-21 fully-abstract-comp/technical-report.tex
First updates to explanatory section about component layout and such.

\subsection{Component layout and linking}
We define a notion of

A target-level program needs a number of things available in order to be able to execute securely. In the following, we list what it needs followed by a description of how they are made available.

A program needs access to the following:
\begin{description}
\item[Code] The instructions of a program should of course be available so they can be executed.
\item[Program seals] Each call/return point of the program needs a unique seal in order to enforce well-bracketedness. This seal needs to be unique on the entire machine.
\item[Stack] A program stores the value of local variables on the stack. 
\item[Persistent data storage] A program may also need to use "global variables" these are stored in a piece of memory separate from the stack.
\item[Linking table] A program may need to call other programs. Other programs are made available in a linking table.
\end{description}

In the following, we describe the setup in detail. Figure~\ref{fig:trg-prog-link} illustrates the setup.

The \emph{code}, \emph{program seals}, and \emph{linking table} are available through a normal read-execute capability in the $\pc$ register. The program seals are found on the first address governed by this capability. The second address governed by the capability contains a normal read capability that governs the linking table and points to the first address. The remaining addresses governed by the capability in the $\pc$ register contain the instructions of the program.

@@

The \emph{persistent data storage} is expected to be accessible through a normal read-write capability in $r_\data$ during normal execution (during a return the stack capability will initially be in the $r_\data$ register, but it should be spliced with the returned stack and moved to the $r_\stk$ register). There are two ways for a program to get this data capability: (1) the data part of the code/data pair (for either a callback or a global function in the linking table) should be the sealed data capability. (2) During a call, the data capability should be stored on the stack, so it can be retrieved afterwards.
\begin{figure}
  \centering
  \includegraphics[angle=90,width=\textwidth]{img/linking.pdf}
  \caption{Linking and program layout.}
  \label{fig:trg-prog-link}
\end{figure}

>>>>

\subsection{Component layout and linking}
\dominique{21-3-2018: TODO: update this section (further) to reflect recent changes.}
A target- or source-level component needs a number of things.
In the following, we list what it needs followed by a description of how they are made available.

A program needs access to the following:
\begin{description}
\item[Code] The instructions of a component should of course be available so they can be executed.
\item[Component seals] Each call/return point of the component, as well as every location where new closures are created, needs a unique seal in order to enforce well-bracketedness.
  This seal needs to be unique on the entire machine.
\item[Stack] A component stores the value of local variables on the stack. 
\item[Persistent data storage] A component may also need to use "global variables" these are stored in a piece of memory separate from the stack.
\item[Access to other components' exported functions] A component may need to call other components.
  Every component makes available a number of exported values (e.g. sealed code-data pairs for invoking certain functions) and components are allowed to include these exported values in their data memory.
  They could, for example, keep a linking table there through which they can invoke other components' exports.
\end{description}

In the following, we describe the setup in detail.
Figure~\ref{fig:trg-prog-link} illustrates the setup (modulo the fact that the code memory contains a reference to the linking table, which is now no longer allowed).

The \emph{code} and \emph{program seals} are available through a normal read-execute capability in the $\pc$ register.
The program seals are stored as part of the code memory and can be accessed through the $\pc$ register.
The data memory may contain references to references exported by other components, organised, for example, as a linking table.
The remaining addresses governed by the capability in the $\pc$ register contain the instructions of the program.

@@

The \emph{persistent data storage} is expected to be accessible through a normal read-write capability in $r_\data$ during normal execution (during a return the stack capability will initially be in the $r_\data$ register, but it should be spliced with the returned stack and moved to the $r_\stk$ register). There are two ways for a program to get this data capability: (1) the data part of the code/data pair (for either a callback or a global function in the linking table) should be the sealed data capability. (2) During a call, the data capability should be stored on the stack, so it can be retrieved afterwards.
\begin{figure}
  \centering
  \includegraphics[angle=90,width=\textwidth]{img/linking.pdf}
  \caption{Linking and program layout (modulo the fact that the code memory contains a reference to the linking table, which is now no longer allowed).}
  \label{fig:trg-prog-link}
\end{figure}
